---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Package `genrs`

<!-- badges: start -->
<!-- badges: end -->

Functions that allow generating random samples from the Pareto I distribution and Burr XII distribution. The method used to generate these values was implemented using the Inverse Transform Sampling method.

## Installation

You can install the development version of genrs from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("wyaravms/genrs")
```

## Example

These are some basic examples using the functions available in the `genrs` package:

```{r example}
library(genrs)
## basic example code
```

Function `rburrxii` that generates random data following a Burr XII distribution with parameters shape1 and shape2.

```{r burrxii}
rburrxii(10, 2, 3)
```

Function `rparetoi` that generates random data following a Pareto I distribution with parameters scale and shape.

```{r paretoi}
rparetoi(10, 5, 2)
```
